%-------------------------
% ATS-Compliant Resume in LaTeX
% Author: Shubham Singh
%-------------------------

\documentclass[a4paper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=0.75in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}

% ATS-friendly settings
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=blue!70!black,
    pdfauthor={Shubham Singh},
    pdftitle={Shubham Singh - Resume},
    pdfsubject={Resume},
}

% Section formatting
\titleformat{\section}{
    \large\bfseries\scshape
}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{16pt}{8pt}

% Remove page numbers
\pagestyle{empty}

% Custom commands
\newcommand{\resumeSubheading}[4]{
    \vspace{4pt}
    \noindent\textbf{#1} \hfill #2 \\
    \textit{#3} \hfill \textit{#4}
    \vspace{2pt}
}

\newcommand{\resumeItem}[1]{
    \item #1
}

\begin{document}

%----------HEADER----------
\begin{center}
    {\LARGE\bfseries Shubham Singh} \\[6pt]
    Mumbai, Maharashtra, India \\[3pt]
    \href{tel:+917021320621}{+91 7021320621} \enspace$|$\enspace
    \href{mailto:singhshubham9295@gmail.com}{singhshubham9295@gmail.com} \enspace$|$\enspace
    \href{https://www.linkedin.com/in/shubhamsingh7576}{linkedin.com/in/shubhamsingh7576}
\end{center}

%----------SUMMARY----------
\section{Summary}
Results-driven planner, strategist, and implementer with 9+ years of experience across e-commerce, telecom, ed-tech, logistics, retention, and KYC sectors. Proficient in quality assurance, operations, and training. Proven track record of enhancing customer satisfaction, improving service quality, strengthening team collaboration, and achieving organisational goals through effective training, coaching, and operational strategies. A confident and adaptable facilitator with strong work ethics, dedicated to driving business success and continuous improvement.

%----------EXPERIENCE----------
\section{Experience}

\resumeSubheading
    {TaskUs}{Navi Mumbai, Maharashtra, India}
    {Learning Experience Manager}{April 2025 -- Present}
\begin{itemize}[leftmargin=0.2in, topsep=2pt, itemsep=1pt, parsep=0pt]
    \resumeItem{Led end-to-end training programmes for Uber's Customer Experience operations, ensuring alignment with client objectives and brand standards.}
    \resumeItem{Tailored and managed training content to align with local needs while tracking compliance, quality, administration, and overall programme effectiveness.}
    \resumeItem{Monitored the performance and success of new hires and evaluated employee progress after training.}
    \resumeItem{Collaborated with stakeholders and facilitated client-facing meetings to ensure alignment and project success.}
    \resumeItem{Acted as the primary point of contact, ensuring smooth communication flow and addressing client inquiries promptly.}
    \resumeItem{Managed process changes and implemented improvements to drive enhanced business outcomes.}
    \resumeItem{Created SOPs to streamline training deliverables.}
    \resumeItem{Curated a library of resources to support continuous learning.}
\end{itemize}

\resumeSubheading
    {Teleperformance}{Mumbai, Maharashtra, India}
    {Training Manager}{June 2024 -- April 2025}
\begin{itemize}[leftmargin=0.2in, topsep=2pt, itemsep=1pt, parsep=0pt]
    \resumeItem{Led comprehensive training initiatives for the Onfido project, specialising in fraud detection and prevention.}
    \resumeItem{Supervised a team of Assistant Managers, Leads, and Trainers, overseeing agent deployment, development, and productivity across multiple locations.}
    \resumeItem{Tailored and managed training content to align with local needs while tracking compliance, quality, administration, and overall programme effectiveness.}
    \resumeItem{Delivered training across teams, implementing strategic interventions at critical milestones.}
    \resumeItem{Monitored the performance and success of new hires and evaluated employee progress after training.}
    \resumeItem{Collaborated with stakeholders and facilitated client-facing meetings to ensure alignment and project success.}
    \resumeItem{Managed process changes and implemented improvements to drive enhanced business outcomes.}
    \resumeItem{Created SOPs to streamline training deliverables.}
    \resumeItem{Successfully participated in and completed internal and external risk and compliance audits.}
\end{itemize}

\resumeSubheading
    {Hexaware Technologies}{Navi Mumbai, Maharashtra, India}
    {Assistant Manager -- Training, Engagement and Development}{July 2023 -- June 2024}
\begin{itemize}[leftmargin=0.2in, topsep=2pt, itemsep=1pt, parsep=0pt]
    \resumeItem{Led comprehensive training for the McAfee project, focusing on retention and upsell business.}
    \resumeItem{Managed training across teams, implementing interventions at key intervals.}
    \resumeItem{Aligned operations and curriculum as a key business partner.}
    \resumeItem{Oversaw quality, administration, and effectiveness of training programmes.}
    \resumeItem{Tracked success of new hires and performance of graduated employees.}
    \resumeItem{Collaborated with stakeholders and conducted client-facing meetings.}
    \resumeItem{Managed process changes and implementations for enhanced business objectives.}
\end{itemize}

\resumeSubheading
    {WNS Global Services}{Pune, Maharashtra, India}
    {Assistant Manager -- Training}{April 2022 -- July 2023}
\begin{itemize}[leftmargin=0.2in, topsep=2pt, itemsep=1pt, parsep=0pt]
    \resumeItem{Managed a team of lead trainers along with Ramp Team Leaders.}
    \resumeItem{Handled the transition of a newly acquired business (FedEx) for Pune and Vizag locations with a headcount of 250 across both sites. Created training planners, transition SOPs, managed end-to-end asset procurement, cross-training, and certification of Trainers and Operations Leads via a third party.}
    \resumeItem{Ensured end-to-end people and performance management for the sites, covering production and quality metrics.}
    \resumeItem{Conducted 5 Whys analysis, RCAs, and action planning involving end-to-end CAPA and close-looping in the training curriculum.}
    \resumeItem{Spearheaded weekly and monthly reviews for Training and Transition Team Leads to identify performance gaps, develop improvement strategies, discuss policy updates, and conduct impact analysis along with process change management.}
    \resumeItem{Ensured all new updates reached the production floor in a timely and productive manner.}
    \resumeItem{Managed client-facing meetings along with all process changes and implementations.}
    \resumeItem{Spearheaded internal and external calibrations across both sites.}
\end{itemize}

\resumeSubheading
    {Concentrix}{Mumbai, Maharashtra, India}
    {Assistant Manager -- Training and Quality}{January 2020 -- April 2022}
\begin{itemize}[leftmargin=0.2in, topsep=2pt, itemsep=1pt, parsep=0pt]
    \resumeItem{Leveraged fair evaluation processes, employee reviews, and staff mentoring to drive performance and job satisfaction at all levels.}
    \resumeItem{Led multiple focus groups to implement new strategies for better TNA and action plan implementation for key deliverables.}
    \resumeItem{Created schedules and managed employee productivity.}
    \resumeItem{Handled quality and training deliverables for international markets.}
    \resumeItem{Managed multiple LOBs involving outbound/inbound calling and chat. Implemented TNA and action plans for key deliverables.}
    \resumeItem{Successfully oversaw onboarding, certification, and operations handover processes.}
\end{itemize}

\resumeSubheading
    {Sutherland}{Mumbai, Maharashtra, India}
    {Process Trainer}{October 2016 -- January 2020}
\begin{itemize}[leftmargin=0.2in, topsep=2pt, itemsep=1pt, parsep=0pt]
    \resumeItem{Managed training for 8 lines of business including outbound, inbound, calling, chat, and email processes under the seller support account for Amazon.}
    \resumeItem{Conducted product and process training for all new hire batches. Delivered floor training and refresher training for tenured agents, Team Leads, SMEs, and Managers.}
    \resumeItem{Managed entire new hire training and performance through to certification.}
    \resumeItem{Prepared weekly client review documents and participated as the training POC in all client meetings.}
    \resumeItem{Served as the POC for all content updates, implementation, and feedback post impact analysis.}
\end{itemize}

%----------EDUCATION----------
\section{Education}

\resumeSubheading
    {University of Mumbai}{}
    {Bachelor of Engineering -- Telecommunications Engineering}{}

%----------SKILLS----------
\section{Skills}
\noindent Service-Level Agreements (SLA) \enspace$|$\enspace Strategic Roadmaps \enspace$|$\enspace Training Leadership \enspace$|$\enspace Quality Assurance \enspace$|$\enspace Operations Management \enspace$|$\enspace Stakeholder Collaboration \enspace$|$\enspace Process Improvement \enspace$|$\enspace Training Needs Analysis (TNA) \enspace$|$\enspace SOP Development \enspace$|$\enspace Performance Management

%----------CERTIFICATIONS----------
\section{Certifications}
\begin{itemize}[leftmargin=0.2in, topsep=2pt, itemsep=1pt, parsep=0pt]
    \resumeItem{WNS Certified Trainer}
    \resumeItem{Certified Specialist Trainer}
    \resumeItem{Sutherland Certified Learning Professional}
\end{itemize}

\end{document}
